---
title: "Chapter 3 Bar Graphics"
author: "Toan"
date: "2016¦~4¤ë16¤é"
output: html_document
---
3.1 Making the Basic Bar Graphics.


```{r}
library(ggplot2)
library(gcookbook)
pg_mean
ggplot(pg_mean, aes(x = group, y = weight)) + geom_bar(stat = "identity")

```


```{r}
# x as continuos and x as factor.
BOD
str(BOD)
ggplot(BOD, aes(x = Time, y = demand)) + geom_bar(stat = "identity")
ggplot(BOD, aes(x = factor(Time), y = demand)) + geom_bar(stat = "identity")
```

```{r}
# change fill colour (fill) and outline (colour)
ggplot(pg_mean, aes(x = group, y = weight))+ geom_bar(stat = "identity", fill = "lightblue", colour = "black")
 
```
3.2. Grouping Bars Together

```{r}
library(gcookbook) # For the data set
cabbage_exp
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
 geom_bar(stat = "identity", position="dodge")
```

```{r}
# Change the colour templete (scale_fill_brewer(palette="Pastel1"))
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
  geom_bar(stat = "identity", position="dodge", colour="black") +
  scale_fill_brewer(palette="Pastel1")
```

3.3. Making a Bar Graph of Counts

```{r}
# Marking a graphing of count ( x only)
head(diamonds)
str(diamonds)
ggplot(diamonds, aes(x = cut)) + geom_bar()
```
3.4. Using Colors in a Bar Graph

```{r}
library(gcookbook) # For the data set
upc <- subset(uspopchange, rank(Change)>40)
upc
ggplot(upc, aes(x=Abb, y=Change, fill=Region)) + geom_bar(stat="identity")
ggplot(upc, aes(x=reorder(Abb, Change), y=Change, fill=Region)) +
geom_bar(stat="identity", colour="black") +
scale_fill_manual(values=c("#669933", "#FFCC66")) +
xlab("State")
#Comment: Change the colour of the bar chart by using scale_fill_manual
```
3.5. Coloring Negative and Positive Bars Differently

```{r}
library(gcookbook) # For the data set
csub <- subset(climate, Source=="Berkeley" & Year >= 1900)
csub$pos <- csub$Anomaly10y >= 0
csub
ggplot(csub, aes(x=Year, y=Anomaly10y, fill=pos)) +
geom_bar(stat="identity", position="identity", colour="black", size=0.25) +
scale_fill_manual(values=c("#CCEEFF", "#FFDDDD"), guide=FALSE)
#Comment: create one more variable pos( TRUE OR FAIL) and use fill the map the colour

```
3.6. Adjusting Bar Width and Spacing

For grouped bar.

```{r}
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
geom_bar(stat="identity", width=0.5, position="dodge")
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
geom_bar(stat="identity", width=0.5, position=position_dodge(0.7))
#Comment: by default grouped bar displayed together, set postion_doge > width for seperatation.

```
3.7. Making a Stacked Bar Graph

```{r}
library(gcookbook) # For the data set
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
geom_bar(stat="identity")
# Comment: we can make stacked bar instead of normal bar chart by
#do not specify postion = dodge.
```

Change the lable to the correct position


```{r}
ggplot(cabbage_exp, aes(x=Date, y=Weight, fill=Cultivar)) +
geom_bar(stat="identity", colour="black") +
guides(fill=guide_legend(reverse=TRUE)) +
scale_fill_brewer(palette="Pastel1")
# Comment: there are two way to do that. one is specify
#order in aes. two is guides(fill=guide_legend(reverse=TRUE))
```
3.8. Making a Proportional Stacked Bar Graph
Need some data manipulation.
```{r}
library(gcookbook) # For the data set
library(dplyr)
ce <- cabbage_exp %>%
  group_by(Date) %>% mutate(percent_weight = Weight/sum(Weight)*100) %>%
  arrange(Date)
ce
ggplot(ce, aes(x=Date, y=percent_weight, fill=Cultivar)) +
geom_bar(stat="identity")
```

We want to do some thing more.
```{r}
ggplot(ce, aes(x=Date, y=percent_weight, fill=Cultivar)) +
geom_bar(stat="identity", colour="black") +
guides(fill=guide_legend(reverse=TRUE)) +
scale_fill_brewer(palette="Pastel1")
# Comment: create outline wiht colour, change lable to correct position
# with guides(fill=guide_legend(reverse=TRUE))
# change default coour by scale_fill_brewer(palette="Pastel1")
```

3.9. Adding Labels to a Bar Graph

```{r}
# Below the top
ggplot(cabbage_exp, aes(x=interaction(Date, Cultivar), y=Weight)) +
geom_bar(stat="identity") +
geom_text(aes(label=Weight), vjust=1.5, colour="white")
```

```{r}
# Above the top
ggplot(cabbage_exp, aes(x=interaction(Date, Cultivar), y=Weight)) +
geom_bar(stat="identity") +
geom_text(aes(label=Weight), vjust=-0.2)
#Comment: 
```

Adjust y limit to be a little higher
```{r}
ggplot(cabbage_exp, aes(x=interaction(Date, Cultivar), y=Weight)) +
geom_bar(stat="identity") +
geom_text(aes(label=Weight), vjust=-0.2) +
ylim(0, max(cabbage_exp$Weight) * 1.05)
# Comment: we adjust y limit by using
#ylim(0, max(cabbage_exp$Weight) * 1.05)
```

```{r}
# Map y positions slightly above bar top - y range of plot will auto-adjust
ggplot(cabbage_exp, aes(x=interaction(Date, Cultivar), y=Weight)) +
geom_bar(stat="identity") +
geom_text(aes(y=Weight+0.1, label=Weight))
#Comment: by using geom_text(aes(y=Weight+0.1, label=Weight))
```
We want to put the number value in the middle of the bar chart
and change to the proper label order.

```{r}
library(dplyr)
library(ggplot2)
library(gcookbook) #for the data
ce <- cabbage_exp %>% group_by(Date) %>%
  mutate(label_y = cumsum(Weight) - 0.5*Weight)
ce
ggplot(ce, aes(x=Date, y=Weight, fill=Cultivar)) +
geom_bar(stat="identity", colour="black") +
  geom_text(aes(y=label_y, label=paste(format(Weight, nsmall=2), "kg")),
size=4) +
guides(fill=guide_legend(reverse=TRUE)) +
scale_fill_brewer(palette="Pastel1")
# Comment: We create one more varialbe label_y
# to index the postion of label
# and using geom_text to print text label.
```

3.10 Marking a Cleveland Dot Plot.
We want to create normal Cleveland Dot Plot
```{r}
library(gcookbook) # For the data set
tophit <- tophitters2001[1:25, ] # Take the top 25 from the tophitters data set
ggplot(tophit, aes(x=avg, y=name)) + geom_point()
```

We want to reorder the y axis (name by the value in x)
```{r}
ggplot(tophit, aes(x=avg, y=reorder(name, avg))) +
geom_point(size=3) + # Use a larger dot
theme_bw() +
theme(panel.grid.major.x = element_blank(),
panel.grid.minor.x = element_blank(),
panel.grid.major.y = element_line(colour="grey60", linetype="dashed"))
# Comment: using the reorder() fucntion to reoder the name.
```
We want to rotate this chart let name in the x axis and avg in the y axis.
```{r}
ggplot(tophit, aes(x=reorder(name, avg), y=avg)) +
geom_point(size=3) + # Use a larger dot
theme_bw() +
theme(axis.text.x = element_text(angle=60, hjust=1),
panel.grid.major.y = element_blank(),
panel.grid.minor.y = element_blank(),
panel.grid.major.x = element_line(colour="grey60", linetype="dashed"))
```
We want to create a Cleveland Dot plot with divied
by to group or factor of lg and also order by avg value.
```{r}
# Create nameorder to index for name in the data set.
nameorder <- tophit$name[order(tophit$lg, tophit$avg)]
#change the name column into factor and also reorder it by nameorder
tophit$name <- factor(tophit$name, levels=nameorder)
ggplot(tophit, aes(x=avg, y=name)) +
geom_segment(aes(yend=name), xend=0, colour="grey50") +
geom_point(size=3, aes(colour=lg)) +
scale_colour_brewer(palette="Set1", limits=c("NL","AL")) +
theme_bw() +
theme(panel.grid.major.y = element_blank(), # No horizontal grid lines
legend.position=c(1, 0.55), # Put legend inside plot area
legend.justification=c(1, 0.5))
# Comment: using geom_segment(aes(yend=name), xend=0, colour="grey50")
# to replace grid line.
```

We want to change lg label in to facet_grid.

```{r}
ggplot(tophit, aes(x=avg, y=name)) +
geom_segment(aes(yend=name), xend=0, colour="grey50") +
geom_point(size=3, aes(colour=lg)) +
scale_colour_brewer(palette="Set1", limits=c("NL","AL"), guide=FALSE) +
theme_bw() +
theme(panel.grid.major.y = element_blank()) +
facet_grid(lg ~ ., scales="free_y", space="free_y")
```

```{r}

```

```{r}

```










