---
title: "Line Chart"
author: "Toan"
date: "2016¦~4¤ë21¤é"
output: html_document
---
##1. Making a Basic Line Graph
We just want to create a simple line chart.

```{r}
library(ggplot2)
ggplot(BOD, aes(x=Time, y=demand)) + geom_line()
```

we want to expadn the y axis to 0.
```{r}
# These have the same result
ggplot(BOD, aes(x=Time, y=demand)) + geom_line() + ylim(0, max(BOD$demand))
ggplot(BOD, aes(x=Time, y=demand)) + geom_line() + expand_limits(y=0)

```

##2. Adding Points to a Line Graph

```{r}
library(gcookbook) # For the data set
library(grid)
library(gridExtra)
library(ggplot2)
p1 <- ggplot(worldpop, aes(x=Year, y=Population)) + geom_line() + geom_point()
# Same with a log y-axis
p2 <- ggplot(worldpop, aes(x=Year, y=Population)) + geom_line() + geom_point() + 
  scale_y_log10()
grid.arrange(p1, p2, ncol = 2)

```

##3. Making a Line Graph with Multiple Lines
we want to map other variable (factor variable) by
colour or shape.

```{r}
library(dplyr)
# Summarize the ToothGrowth data
tg <- ToothGrowth %>% group_by(supp, dose) %>%
  summarize(length=mean(len))
tg
# Map supp to colour
p1 <- ggplot(tg, aes(x=dose, y=length, colour=supp)) + geom_line()
# Map supp to linetype
p2 <- ggplot(tg, aes(x=dose, y=length, linetype=supp)) + geom_line()
grid.arrange(p1, p2, ncol = 2)


```

if x is a factor variable, we have to let r know what factor we want to group.
```{r}
ggplot(tg, aes(x=factor(dose), y=length, colour=supp, group=supp)) + geom_line()
#Comment: we map supp variable by colour and also sepecify group=supp.
#to let R know which factor you want to group.
```
We want to change to size of point and colour of the point.
```{r}
p1 <- ggplot(tg, aes(x=dose, y=length, shape=supp)) + geom_line() +
geom_point(size=4) # Make the points a little larger
p2 <- ggplot(tg, aes(x=dose, y=length, fill=supp)) + geom_line() +
geom_point(size=4, shape=21) # Also use a point with a color fill
grid.arrange(p1, p2, ncol = 2)
#Comment: increase size of point by geom_point(size=4)
#set different colour for point of different level of factor by.
#fill=supp and set the shape which shape have fill.


```

We want move line and point a little. 
```{r}
ggplot(tg, aes(x=dose, y=length, shape=supp)) +
geom_line(position=position_dodge(0.2)) + # Dodge lines by 0.2
geom_point(position=position_dodge(0.2), size=4) # Dodge points by 0.2
```

##4. Changing the Appearance of Lines

```{r}
ggplot(BOD, aes(x=Time, y=demand)) +
geom_line(linetype="dashed", size=1, colour="blue")
```

We want to change the colour of the line.
```{r}
library(dplyr)
# Summarize the ToothGrowth data
tg <- ToothGrowth %>% group_by(supp, dose) %>%
  summarize(length=mean(len))
ggplot(tg, aes(x=dose, y=length, colour=supp)) +
geom_line() +
scale_colour_brewer(palette="Set1")

```

We want to set specific colour for line or change different colour of the shape by fill.
```{r}
# If both lines have the same properties, you need to specify a variable to
# use for grouping
 p1 <- ggplot(tg, aes(x=dose, y=length, group=supp)) +
geom_line(colour="darkgreen", size=1.5)
# Since supp is mapped to colour, it will automatically be used for grouping
p2 <- ggplot(tg, aes(x=dose, y=length, colour=supp)) +
geom_line(linetype="dashed") +
geom_point(shape=22, size=3, fill="white")
grid.arrange(p1, p2, ncol = 2)
#Comment: because supp was mapping by colour so the line colour will automatic change.

```

##5. Changing the Appearance of Points
We want to sepcify point properties in geom_point()

```{r}
p1 <- ggplot(BOD, aes(x=Time, y=demand)) +
geom_line() +
geom_point(size=4, shape=22, colour="darkred", fill="pink")
p2 <- ggplot(BOD, aes(x=Time, y=demand)) +
geom_line() +
geom_point(size=4, shape=21, fill="white")
grid.arrange(p1, p2, ncol = 2)
```

```{r}
library(dplyr)
# Summarize the ToothGrowth data
tg <- ToothGrowth %>% group_by(supp, dose) %>%
  summarize(length=mean(len))
pd <- position_dodge(0.2)
ggplot(tg, aes(x=dose, y=length, fill=supp)) +
geom_line(position=pd) +
geom_point(shape=21, size=3, position=pd) +
scale_fill_manual(values=c("black","white"))
```

##6. Making a Graph with a Shaded Area

```{r}
sunspotyear <- data.frame(
Year = as.numeric(time(sunspot.year)),
Sunspots = as.numeric(sunspot.year)
)
ggplot(sunspotyear, aes(x=Year, y=Sunspots)) + geom_area()
#Comment: using geom_area() to draw shaded shape under the line.
```

We want to specify colour ( colour of the line) + fill (colour of the shaded part)
alpha the transparent.
```{r}
p1 <- ggplot(sunspotyear, aes(x=Year, y=Sunspots)) +
geom_area(colour="black", fill="blue", alpha=.2)
p2 <- ggplot(sunspotyear, aes(x=Year, y=Sunspots)) +
geom_area(fill="blue", alpha=.2) +
geom_line()
grid.arrange(p1, p2, ncol = 2)
  
```

##7. Making a Stacked Area Graph
We want to make stacked are graph buy specify fill in aes and + geom_area()
```{r}
library(gcookbook) # For the data set
p1 <- ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) + geom_area()
#dd line and change colour
p2 <- ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup)) +
geom_area(colour="black", size=.2, alpha=.4) +
scale_fill_brewer(palette="Blues", breaks=rev(levels(uspopage$AgeGroup)))
grid.arrange(p1, p2, ncol = 2)

```

We want to add line and change the oder of Age Group.
```{r}
ggplot(uspopage, aes(x=Year, y=Thousands, fill=AgeGroup, order=desc(AgeGroup))) +
geom_area(colour=NA, alpha=.4) +
scale_fill_brewer(palette="Blues") +
geom_line(position="stack", size=.2)
```

##8. Making a Proportional Stacked Area Graph

```{r}
library(gcookbook)
library(dplyr)
uspopage_prop <- uspopage %>% group_by(Year) %>%
  mutate(Percent = Thousands / sum(Thousands) * 100)
ggplot(uspopage_prop, aes(x=Year, y=Percent, fill=AgeGroup)) +
geom_area(colour="black", size=.2, alpha=.4) +
scale_fill_brewer(palette="Blues", breaks=rev(levels(uspopage$AgeGroup)))
#Comment: you create one more Percent variable to draw 

```

##9. Adding a Confidence Region
Use geom_ribbon() and map values to ymin and ymax.

```{r}
clim <- climate %>% filter(Source == "Berkeley") %>%
+ select(Year, Anomaly10y, Unc10y)
head(clim)
p1 <- ggplot(clim, aes(x=Year, y=Anomaly10y)) +
geom_ribbon(aes(ymin=Anomaly10y-Unc10y, ymax=Anomaly10y+Unc10y),
alpha=0.2) +
geom_line()
p2 <- ggplot(clim, aes(x=Year, y=Anomaly10y)) +
geom_line(aes(y=Anomaly10y-Unc10y), colour="grey50", linetype="dotted") +
geom_line(aes(y=Anomaly10y+Unc10y), colour="grey50", linetype="dotted") +
geom_line()
grid.arrange( p1, p2, ncol = 2)
#Comment: or you can two dottted line and one line


```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
